ODGI: understanding pangenome graphs

### 2021-11-07 manuscript/main.tex
maybe the famous author isn't needed

\title[ODGI: understanding pangenome graphs]{ODGI: understanding pangenome graphs}
\author[Guarracino, Heumos \textit{et~al}.]{
Andrea~Guarracino\,$^{\text{\sfb 1} \dagger}$,
Simon~Heumos\,$^{\text{\sfb 2} \dagger}$,
Sven~Nahnsen\,$^{\text{\sfb 2,3}}$,
Human Pangenome Reference Consortium,
Pjotr~Prins\,$^{\text{\sfb 4}}$,
and~Erik~Garrison\,$^{\text{\sfb 4}*}$
}

\address{
$^{\text{\sf 1}}$Genomics Research Centre, Human Technopole, Milan, Italy \\
$^{\text{\sf 2}}$Quantitative Biology Center (QBiC), University of T\"ubingen, T\"ubingen, Germany, 72076 \\
$^{\text{\sf 3}}$Biomedical Data Science, Dept. of Computer Science, University of T\"ubingen, T\"ubingen, Germany, 72076 \\
%$^{\text{\sf 4}}$\url{https://humanpangenome.org/} \\
$^{\text{\sf 4}}$University of Tennessee Health Science Center, Memphis, TN, USA
}

>>>>

\title[ODGI: understanding pangenome graphs]{ODGI: understanding pangenome graphs}
\author[Guarracino, Heumos \textit{et~al}.]{
Andrea~Guarracino\,$^{\text{\sfb 1} \dagger}$,
Simon~Heumos\,$^{\text{\sfb 2} \dagger}$,
Sven~Nahnsen\,$^{\text{\sfb 2,3}}$,
Pjotr~Prins\,$^{\text{\sfb 4}}$,
and~Erik~Garrison\,$^{\text{\sfb 4}*}$
}

\address{
$^{\text{\sf 1}}$Genomics Research Centre, Human Technopole, Milan, Italy \\
$^{\text{\sf 2}}$Quantitative Biology Center (QBiC), University of T\"ubingen, T\"ubingen, Germany, 72076 \\
$^{\text{\sf 3}}$Biomedical Data Science, Dept. of Computer Science, University of T\"ubingen, T\"ubingen, Germany, 72076 \\
$^{\text{\sf 4}}$University of Tennessee Health Science Center, Memphis, TN, USA
}
